From DSL to HPC Component-Based Runtime: A Multi-Stencil DSL Case Study

### 2016-01-20 ARTICLES/RR/rapport_v0/csm.tex
clean Helene 20/01/2016

%-------------------------------------
\subsection{Phase, group and kernel}
Using the formalism described in Sections~\ref{sect:formalism} and~\ref{sect:component}, the following definitions are given for the solution.

@@

One can notice, however, that in a phase $Phi$ of a stencil program it is possible to have a pair $c_i,c_j \in \Phi$, which verifies $c_i<c_j$. As a result, a phase is equivalent to a sequence of computations $SEQ$. The set of phases of a stencil program are ordered and a synchronization is needed between two different \emph{phases} of a stencil program $\mathcal{P}$. In other terms for two phases $\Phi_1$ and $\Phi_2$ $\exists c_i \in \Phi_1, c_j \in \Phi_2$ such that $c_i \ll c_j$. If $m$ is the number of stencil computations in a phase $\Phi_i$ among $n$ total computations, the synchronizations of $\Phi_i$ are applied on $\bigcup_{j=0}^{m-1}R_j$.

Instead of introducing an additional definition for the equivalent of $SSEQ$, and because $sequence(sequence(a,b),sequence(c,d))=sequence(a,b,c,d)$, synchronizations needed by a new phase are commputed inside the Phase itself before computations. A phase component is defined as
\begin{equation}
Phase(\{provide,use-multiple, synchronization\},\{phase\}).
\end{equation}
 The function $phase$ performs the needed synchronizations before to use each component of the sequence

@@

Thus, a dependency exists between two different \emph{groups} of a stencil program $\mathcal{P}$, but the computations inside a \emph{group} are unordered, without dependencies. As a result, the Group component is defined as $PAR$
\begin{equation}
Group(\{provide,use-multiple\},\{group\}),
\end{equation}
 where the function $group$ creates a thread for each component to use, and join all threads at the end.

\begin{algorithm}[H]
 \ForAll{component $cp$ to use}{
 create thread $t$
 $t$ uses the provide interface of $cp$
 }
 join all threads
 \label{alg:par}
 \caption{group function}
 \end{algorithm}

@@

\begin{algorithm}[H]
 \ForAll{elements $d$ in $D$}{
 $w(d)=e_1(R(d),R(\mathcal{N}(d)))$\\
 $w(d)=e_2(R(d),R(\mathcal{N}(d)))$\\
 ...
 }
 \caption{kernel function}
 \end{algorithm}

\medskip
The component assembly of the computations of a mesh-based numerical simulation using phase, group and kernel components is represented in the Figure~\ref{phgpk}. This assembly is equivalent to the one presented in the Figure~\ref{approx}, but $SSEQ$ and $SEQ$ are fusionned in $phase$, and the component $kernel$ is bit different from $K$.

@@

This component assembly of computations can be, by definition, extracted from an ordered list of typed computations $s(R,w,D,e,\mathcal{N})$ or $l(R,w,D,e)$. $R$, $w$ and $D$ are used to build Phases, Groups and Kernels, while $e$ and $\mathcal{N}$ are used inside the Kernel components. As a result, we can define a function $\lambda$ to build the computation assembly
\begin{equation}
\lambda : list_o(c(R,w,D,e)) \rightarrow \alpha ({{Phase},{Group},{Kernel}},L,R)
\end{equation}

%-------------------------------------
\subsection{Overall assembly}

\paragraph{The SIPSim model.} The SIPSim model~\cite{} is a model which proposes a systematic way to create an SPMD implicit parallelism solution for mesh-based numerical simulations through four concepts. The first concept is a \textit{Distributed Data Structure} (DDS), which represents the distributed mesh. Thus, the DDS manages a domain decomposition, or more broadly a graph partitioning problem which balances the number of elements on available resources, and which tries to minimize the number of needed synchronizations between resources. It has to be noticed that this particular task could be managed by an external graph partitionner. In addition to this, the DDS also has to offer an efficient access to an element of a mesh and to its neighborhood. The second concept is the \textit{Distributed Property Map} (DPMap), which is responsible to map a quantity to simulate (a data) onto the distributed mesh. The third concept is an \textit{applicator}, which is responsible for applying a set of synchronizations before a set of numerical computations written by the user (also called operations). Finally, the last concept contains the \textit{interfaces} needed to write an operation in a sequential programming style while using DPMaps mapped onto the DDS. Those interfaces are directly linked to the type of DDS used.

\paragraph{CSM overall assembly.} From the SIPSim model, CSM uses the concept of DDS and DPMap and transforms them in components to build the overall component assembly. The implementation of those components are not described in this paper, and it is possible to imagine an adhoc implementation in simple cases, as a Cartesian mesh, or existing external implementations (libraries) in more complex cases. This choice is an implementation choice and will be compatible with CSM. In addition to those two new components, the concept of \textit{interface} of the SIPSim model has to be kept to write the implementation of the expressions $e$ of the numerical computations on distributed data structures. But this concept is not needed as a component. It could be provided by the DDS itself or it could be introduced as a header file for example.

The overall assembly produced by the model is presented in the Figure~\ref{csmassembly}. First, the component \textit{DDS} and the component \textit{Data}, which corresponds to the DPMap concept of the SIPSim model, are introduced in the assembly with the same functionnality than described above.

Second, one can notice that the assembly described in the previous Figure~\ref{phgpk} is, of course, inserted in the overall assembly. However, even if the \textit{Phase} component is still responsible for starting a set of synchronizations, those synchronizations are in fact performed by the \textit{Connector} component. Actually, the \textit{Phase} component uses the data concerned by its synchronizations, and then each data uses the \textit{Connector}, which finally performs the synchronizations. As a result, the \textit{Connector} component can be implemented with threads, or with MPI, without the modification of \textit{Phase} and \textit{Data} components. This is a separation of concerns between the data of the simulation and the parallelization strategy which increases the portability of the application. This strategy has been more described in the paper~\cite{}.

The third important point to notice is the introduction of the component \textit{Time} which is responsible for the time iteration steps of the simulation. To establish the end of time steps, most of the time a convergence function is computed on data, but it also happens that a fix number of iterations is precised. For this reason, the instanciation of the component \textit{Convergence} is optional. The \textit{Driver} component starts the simulation and launches the initialization of the DDS, and the \textit{DrApp} component starts the initialization of the data and also the time loop of the simulation. Finally, the \textit{Initializer} component is linked to the initialization of data (read a file format, default value, or numerical computation). The computation components, specific to each simulation, are \textit{Kernel} and \textit{Convergence}, and to perform numerical expressions $e$ those components have to be connected to the Data of each $R$ and $w$.

%---------
\begin{figure}[h!]
\begin{center}
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (phase) at (0,0) {Phase};
   \node[component] (group) [right=of phase] {Group};
   \node[component] (kernel) [right=of group] {Kernel};
   \node[component] (init) [above=1.5cm of group] {Initializer};
   \node[component] (data) [above=1.5cm of phase] {Data};
   \node[component] (time) [left=of phase] {Time};
   \node[component] (drapp) [above=1.5cm of time] {DrApp};
   \node[dcomponent] (conv) [left=of time] {Convergence};
   \node[component] (dr) [above=1.5cm of drapp] {Driver};
   \node[component] (dds) [above=1.5cm of data] {DDS};
   \node[component] (connec) [above=1.5cm of init] {Connector};

  \path[->]
  	(dr)		edge  [connection]	node	{}	(dds)
  	(dr)		edge  [connection]	node	{}	(drapp)
  	(drapp)		edge  [connection]	node	{1,n}	(data)
  	(drapp)		edge  [connection]	node	{}	(time)
  	(data)  	edge  [connection]	node	{}	(dds)
  	(data)  	edge  [connection]	node	{}	(connec)
  	(connec)	edge  [connection]	node	{}	(dds)
  				edge  [mpiconn]		node	{}	(4,3)
  	(data)		edge  [connection]	node	{1,n}	(init)
  	(time)		edge  [connection]	node	{}	(conv)
  	(time)		edge  [connection]	node	{1,n}	(phase)
  	(phase)		edge  [connection]	node	{1,n}	(data)
  	(phase)		edge  [connection]	node	{1,n}	(group)
  	(phase)		edge  [bend right=50,connection]   node  [swap]   {1,n}   (kernel)
  	(group)		edge  [connection]	node	{1,n}	(kernel)
  	(kernel)	edge  [connection]	node	{1,n}	(data)
  	(conv)	edge  [connection,dashed]	node	{1,n}	(data);
\end{tikzpicture}
\caption{Overall assembly of the Component Stencil Model.}
\label{csmassembly}
\end{center}
\end{figure}

This overall assembly can be compiled from a set of sequential and descriptive information. First an unordered list of data is needed. A data is defined as
\begin{equation}
data(init_f,E_i,type)
\end{equation}
, where $init_f$ is the function to initialize the data (in the Initializer component), $Ei$ is the set of elements of the mesh on which the data is applied, and $type$ is the actual type of data ($int$, $double$ etc.).

The second needed information is the description of the mesh to use as
\begin{equation}
mesh(type,dimension,size)
\end{equation}
, where $type$ of is the topology of the mesh (for example Cartesian or k-sided unstructured meshes), $dimension$ is the dimension of the mesh, and $size$ is the size of the mesh.

As a result, we can define a function $\Lambda$ to build the overall simulation assembly of the Figure~\ref{csmassembly} as
\begin{equation}
\Lambda : list_o(c(R,w,D,e)) \times list(data(init_f,E_i,type)) \times mesh(type,dimension,size) \rightarrow \alpha (\mathcal{C},L,R)
\end{equation}

The needed information of the function $Lambda$ are typically produced by numericians who try to solve a set of partial differential equations by existing numerical methods, by a combination of methods, or by their own methods. Once the parallel assembly $\alpha$ is created, the engineer or a numerican developper of the lab can write the set of numerical computation components $Kernel$, the set of $Initializer$ components, and eventually the $Convergence$ component. All those components are written with an imperative sequential programming style using the interfaces linked to the DDS. As a result, multiple levels of separation of concerns are introduced. First the separation of concerns between the numerician and the person in charge of the implementation, and second the separation of concerns between the implementation and the parallelization of the simulation, which is generated.

%\paragraph{Evaluation.}
% for different kind of mesh

>>>>

%-------------------------------------
\subsection{Phase, group and kernel}
Using the formalism described in the Section~\ref{sect:formalism}, the following definitions are given for the solution.

@@

One can notice, however, that in a phase $Phi$ of a stencil program it is possible to have a pair $c_i,c_j \in \Phi$, which verifies $c_i<c_j$. As a result, a phase is equivalent to a sequence of computations $SEQ$. The set of phases of a stencil program are ordered and a synchronization is needed between two different \emph{phases} of a stencil program $\mathcal{P}$. In other terms for two phases $\Phi_1$ and $\Phi_2$ $\exists c_i \in \Phi_1, c_j \in \Phi_2$ such that $c_i \ll c_j$. If $m$ is the number of stencil computations in a phase $\Phi_i$ among $n$ total computations, the synchronizations of $\Phi_i$ are applied on $\bigcup_{j=0}^{m-1}R_j$. Instead of introducing an additional definition for the equivalent of $SSEQ$, and because $sequence(sequence(a,b),sequence(c,d))=sequence(a,b,c,d)$, synchronizations needed by a new phase are commputed inside the Phase itself before computations. A phase component is defined as
\begin{equation}
Phase(\{provide,use-multiple, synchronization\},\{phase\}).
\end{equation}
 The function $phase$ performs the needed synchronizations before to use each component of the sequence

@@

Thus, a dependency exists between two different \emph{groups} of a stencil program $\mathcal{P}$, but the computations inside a \emph{group} are unordered, without dependencies. As a result, the Group component is equivalent to $PAR$.

@@

\begin{algorithm}[H]
 \ForAll{elements $d$ in $D$}{
 $w(d)=e_1(R(d),R(\mathcal{N}(d)))$\\
 $w(d)=e_2(R(d),R(\mathcal{N}(d)))$\\
 ...
 }
 \caption{phase function}
 \end{algorithm}

\medskip
The component assembly of a mesh-based numerical simulation using phase, group and kernel components is represented in the Figure~\ref{phgpk}. This assembly is equivalent to the one presented in the Figure~\ref{approx}, but $SSEQ$ and $SEQ$ are fusionned in $phase$, and the component $kernel$ is bit different from $K$.

@@

%-------------------------------------
\subsection{Overall assembly and evaluation}

### 2016-01-20 ARTICLES/WOLFHPC15/presentation/slides.tex
clean Helene 20/01/2016

% INTRODUCTION / MOTIVATION
%-------------------------------------------------------------
\begin{frame}
\frametitle{Motivation} % HPC DSL
\begin{block}{+ Domain Specific Languages}
\begin{itemize}
\item Separation of concerns (domain/implementation)
\item Easy language for the user
\item Implicit optimizations
\item Implicit parallelization
\end{itemize}
\end{block}
\begin{alertblock}{- Domain Specific Languages}
\begin{itemize}
\item Difficulties deported to the DSL designer
\begin{itemize}
\item Low level high performance programming
\item Maintainability and portability
\end{itemize}
\item As many DSLs as domains
\begin{itemize}
\item DSL composition ?
\end{itemize}
\end{itemize}
\end{alertblock}
\end{frame}
%-------------------------------------------------------------
\begin{frame}
\frametitle{Motivation} % components
\begin{block}{Component models}
\begin{itemize}
\item Divide an application into several independent black boxes
\item Each component defines its interactions with outer world
\item Application = Assembly of components
\end{itemize}
\end{block}
\begin{block}{+ Component models}
\begin{itemize}
\item Maintainability through separation of concerns
\item Code-reuse and productivity
\item Dynamic assembly of components
\end{itemize}
\end{block}
\end{frame}
%-------------------------------------------------------------
\begin{frame}
\frametitle{Motivation} % components
What if a DSL produces a component-based runtime ?

@@

\begin{lstlisting}[style=base]
@mesh:@ cart
@mesh entities:@ cell@,@edgex
@computation domains:@
  allcell @in@ cell
  alledgex @in@ edgex
@data:@
  A@,@cell
  C@,@edgex
@time:@500
@computations:@
  A@[@allcell@]@=&comp&@(@C@[@n1@]@@)@
\end{lstlisting}
\end{column}
\end{columns}
\end{frame}

@@

%----------------
\begin{frame}
\frametitle{Multi-Stencil Language}
\begin{alertblock}{MSL is not}
\begin{itemize}
\item a new stencil optimizer/compiler
\item a new distributed data structure
\end{itemize}
\end{alertblock}
\begin{block}{MSL is}
\begin{itemize}
\item a high-level language for multi-stencil simulations
\item agnostic from the type of mesh used (data structure)
\item based on identifiers only
\end{itemize}
\end{block}
\begin{center}
\textit{MSL produces a "ready-to-fill"\\component-based parallel scheduling of the simulation}
\end{center}
\end{frame}
%----------------

%----------------
\begin{frame}
\frametitle{Related Work}
\begin{block}{Complementary work}
\begin{itemize}
\item Distributed data structures: SkelGIS, Global Arrays
\item Stencil DSLs (on grids): Pochoir, PATUS
\item Stencil DSLs (on unstructured meshes): OP2, Liszt
\end{itemize}
\end{block}
\begin{alertblock}{Similar work}
\begin{itemize}
\item The SIPSim model (DDS,Data,applicators and iterators)
\begin{itemize}
\item Abstraction of a distributed data structure
\end{itemize}
\item Pipeline of stencil computations for image processing: Halide
\begin{itemize}
\item On grids (image), different abstraction level
\end{itemize}
\item DSL to component-based runtime: ?
\end{itemize}
\end{alertblock}
\end{frame}
%----------------
%-------------------------------------------------------------

@@

%----------------
\begin{frame}
\frametitle{MSL to Component-based runtime}
\begin{block}{Ready-to-fill parallel scheduling: mid-grain parallelism}
\begin{itemize}
\item Data parallelism
\begin{itemize}
\item External distributed data structure
\item Automatic detection of synchronizations
\end{itemize}
\item Task parallelism
\begin{itemize}
\item Compile a static scheduling of computation kernels
\end{itemize}
\end{itemize}
\end{block}
The fine grain parallelism is left to other languages: 
\begin{itemize}
\item OpenMP in the kernels
\item Kernels generated by stencil compilers for CPU or GPU (Pochoir, Liszt etc.)
\end{itemize}
\end{frame}
%----------------

@@

%-------------------------------------------------------------
\section{Compiler}
% A slide example MS, 6 slides on graph transformations
%-------------------------------------------------------------
\subsection{Compiler}
%----------------
\begin{frame}[fragile]
\frametitle{Example}
\begin{columns}
\begin{column}{.52\textwidth}
\begin{lstlisting}[style=base]
@mesh:@ cart
@mesh entities:@ cell,edgex,edgey
@computation domains:@
  allcell @in@ cell
  alledgex @in@ edgex
  alledgey @in@ edgey
  part1edgex @in@ edgex
  part2edgex @in@ edgex
@data:@
  a,cell
  b,cell
  c,edgex
  d,edgex
  e,edgey
\end{lstlisting}
\end{column}
\begin{column}{.48\textwidth}
\begin{lstlisting}[style=base]
  f,cell
  g,edgey
  h,edgex
  i,cell
  j,edgex
@time:@500
@computations:@
  b[allcell]=&c0&(a)
  c[alledgex]=&c1&(b[n1])
  d[alledgex]=&c2&(c)
  e[alledgey]=&c3&(c)
  f[allcell]=&c4&(d[n1])
  g[alledgey]=&c5&(e)
  h[alledgex]=&c6&(f)
  i[allcell]=&c7&(g,h)
  j[partedgex]=&c8&(i[n1])
\end{lstlisting}
\end{column}
\end{columns}
\end{frame}
%----------------

@@

  \path[->]
    (s0) edge node {} (c0)
         edge node {} (star1)
         edge node {} (c1)
         edge node {} (p0)
         edge node {} (c7)
         edge node {} (star8)
         edge node {} (c8)
    (p0) edge node {} (s1)
         edge node {} (s2)
    (s1) edge node {} (c2)
         edge node {} (star4)
         edge node {} (c4)
         edge node {} (c4)
         edge node {} (c6)
    (s2) edge node {} (c3)
         edge node {} (c5);
  \end{tikzpicture}
  }
\end{center}
\end{column}
\begin{column}{.52\textwidth}

\end{column}
\end{columns}
\end{frame}
%----------------

  \path[->]
    (s0) edge node {} (c0)
         edge node {} (star1)
         edge node {} (c1)
         edge node {} (p0)
         edge node {} (c7)
         edge node {} (star8)
         edge node {} (c8)
    (p0) edge node {} (s1)
         edge node {} (s2)
    (s1) edge node {} (c2)
         edge node {} (star4)
         edge node {} (c4)
         edge node {} (c4)
         edge node {} (c6)
    (s2) edge node {} (c3);
  \end{tikzpicture}
  }
\end{center}
\end{column}
\begin{column}{.52\textwidth}
\end{column}
\end{columns}
Loop fusion optimization possible
\end{frame}
%----------------

@@

%----------------
\begin{frame}
\frametitle{Resume}
The MSL compiler can produce:
\begin{itemize}
\item A data parallel pattern of the multi-stencil application
\item \textcolor{gray}{An hybrid (data + task) pattern of the multi-stencil application}
\end{itemize}
\end{frame}
%----------------

@@

%-------------------------------------------------------------
\section{Conclusion and perspectives}
%-------------------------------------------------------------
\subsection{Conclusion and perspectives}
\begin{frame}
\frametitle{Conclusion}
\begin{block}{Conclusion}
\begin{itemize}
\item A DSL for Multi-Stencil applications (MSL)
\item The compilation of MSL to get a parallel scheduling pattern of the simulation
\begin{itemize}
\item Data parallelism
\item Task parallelism
\end{itemize}
\item The dump to a component-based runtime
\item Data parallelism evaluation: no overhead introduced 
\end{itemize}
\end{block}
\end{frame}
%-------------------------------------------------------------

%-------------------------------------------------------------
\begin{frame}
\begin{block}{Perspectives}
\frametitle{Perspectives}
\begin{itemize}
\item Improvment of the language (convergence criteria, reduction etc.)
\item Scalability up to $32k$ cores on TGCC Curie (CEA)
\begin{itemize}
\item Compared with SkelGIS and MPI only
\end{itemize}
\item Evaluations on Data+Task parallelism
\begin{itemize}
\item OpenMP 3 inside kernels
\end{itemize}
\item Dynamic scheduling
\begin{itemize}
\item OpenMP 4 with a scheduling component (libgomp)
\item Kstar for StarPU and XKaapi runtimes
\end{itemize}
\item CPU+GPGPUs using stencil compilers (Pochoir, PATUS etc.)
\end{itemize}
$\hookrightarrow$ Show portability, maintainability introduced by components
\end{block}
\end{frame}
%-------------------------------------------------------------

>>>>

% INTRODUCTION / MOTIVATION
%-------------------------------------------------------------
\begin{frame}
\frametitle{Motivation} % HPC DSL
\begin{block}{+ Domain Specific Languages}
\begin{itemize}
\item Separation of concerns (domain/implementation)
\item Easy language for the user
\item Implicit optimizations
\item Implicit parallelization
\end{itemize}
\end{block}
\begin{alertblock}{- Domain Specific Languages}
\begin{itemize}
\item Difficulties deported to the DSL designer
\begin{itemize}
\item Low level high performance programming
\item Maintainability and portability
\end{itemize}
\item As many DSLs as domains
\end{itemize}
\end{alertblock}
\end{frame}
%-------------------------------------------------------------
\begin{frame}
\frametitle{Motivation} % components
\begin{block}{Component models}
\begin{itemize}
\item Divide an application into several independent black boxes
\item Each component defines its interactions with outer world
\item Application = Assembly of components
\end{itemize}
\end{block}
\begin{block}{+ Component models}
\begin{itemize}
\item Maintainability through separation of concerns
\item Code-reuse and productivity
\item Dynamic assembly of components
\end{itemize}
\end{block}
\end{frame}
%-------------------------------------------------------------
\begin{frame}
\frametitle{Motivation} % components
What if a DSL produces a component-based runtime ?

@@

\begin{lstlisting}[style=base]
@mesh:@ cart
@mesh entities:@ cell,edgex
@computation domains:@
  allcell in cell
  alledgex in edgex
@data:@
  A,cell
  C,edgex
@time:@500
@computations:@
  A[allcell]=&comp&(C[n1])
\end{lstlisting}
\end{column}
\end{columns}
\end{frame}

@@

%----------------
\begin{frame}
\frametitle{Multi-Stencil Language}
\begin{alertblock}{MSL is not}
\begin{itemize}
\item a new stencil optimizer/compiler
\item a new distributed data structure
\end{itemize}
\end{alertblock}
\begin{block}{MSL is}
\begin{itemize}
\item a high-level language for multi-stencil simulations
\item agnostic from the type of mesh used (data structure)
\item based on identifiers only
\end{itemize}
\end{block}
\begin{center}
\textit{MSL produces a ready-to-fill\\component-based parallel pattern of the simulation !}
\end{center}
\end{frame}
%----------------

%----------------
\begin{frame}
\frametitle{Related Work}
\begin{block}{Complementary work}
\begin{itemize}
\item Distributed data structures: SkelGIS, Global Arrays
\item Stencil DSLs (on grids): Pochoir, PATUS
\item Stencil DSLs (on unstructured meshes): OP2, Liszt
\end{itemize}
\end{block}
\begin{alertblock}{Similar work}
\begin{itemize}
\item Pipeline of stencil computations for image processing: Halide
\begin{itemize}
\item On grids (image), different abstraction level
\end{itemize}
\item DSL to component-based runtime: ?
\end{itemize}
\end{alertblock}
\end{frame}
%----------------
%-------------------------------------------------------------

@@

%----------------
\begin{frame}
\frametitle{MSL to Component-based runtime}
\begin{block}{Ready-to-fill parallel pattern}
\begin{itemize}
\item Data parallelism
\begin{itemize}
\item External distributed data structure
\item Automatic detection of synchronizations
\end{itemize}
\item Task parallelism (mid-grain)
\begin{itemize}
\item Compile a static scheduling of computation kernels
\end{itemize}
\end{itemize}
\end{block}
The fine grain task parallelism is left to other languages: 
\begin{itemize}
\item OpenMP in the kernels
\item Kernels generated by stencil compilers (Pochoir, PATUS, Liszt etc.)
\end{itemize}
\end{frame}
%----------------

@@

%-------------------------------------------------------------
\section{Compiler}
% A slide example MS, 6 slides on graph transformations
%-------------------------------------------------------------
\subsection{Compiler}
%----------------
\begin{frame}[fragile]
\frametitle{Example}
\begin{columns}
\begin{column}{.52\textwidth}
\begin{lstlisting}[style=base]
@mesh:@ cart
@mesh entities:@ cell,edgex,edgey
@computation domains:@
  allcell in cell
  alledgex in edgex
  alledgey in edgey
  part1edgex in edgex
  part2edgex in edgex
@data:@
  a,cell
  b,cell
  c,edgex
  d,edgex
  e,edgey
\end{lstlisting}
\end{column}
\begin{column}{.48\textwidth}
\begin{lstlisting}[style=base]
  f,cell
  g,edgey
  h,edgex
  i,cell
  j,edgex
@time:@500
@computations:@
  b[allcell]=&c0&(a)
  c[alledgex]=&c1&(b[n1])
  d[alledgex]=&c2&(c)
  e[alledgey]=&c3&(c)
  f[allcell]=&c4&(d[n1])
  g[alledgey]=&c5&(e)
  h[alledgex]=&c6&(f)
  i[allcell]=&c7&(g,h)
  j[partedgex]=&c8&(i[n1])
\end{lstlisting}
\end{column}
\end{columns}
\end{frame}
%----------------

@@

  \path[->]
    (s0) edge node {} (c0)
         edge node {} (star1)
         edge node {} (c1)
         edge node {} (p0)
         edge node {} (c7)
         edge node {} (star8)
         edge node {} (c8)
    (p0) edge node {} (s1)
         edge node {} (s2)
    (s1) edge node {} (c2)
         edge node {} (star4)
         edge node {} (c4)
         edge node {} (c4)
         edge node {} (c6)
    (s2) edge node {} (c3)
         edge node {} (c5);
  \end{tikzpicture}
  }
\end{center}
\end{column}
\begin{column}{.52\textwidth}
\begin{block}{Specific components}
\begin{itemize}
\item $SEQ$ to directly replace $\mathcal{S}$ nodes
\item $PAR$ to directly replace $\mathcal{P}$ nodes
\item $SYNC$ for synchronizations
\item $K$ for computation kernels
\end{itemize}
\end{block}
\end{column}
\end{columns}
\end{frame}
%----------------

@@

%----------------
\begin{frame}
\frametitle{Resume}
The MSL compiler can produces :
\begin{itemize}
\item A data parallel pattern of the multi-stencil application
\item An hybrid (data + task) pattern of the multi-stencil application
\end{itemize}
\end{frame}
%----------------

%----------------
\begin{frame}
\frametitle{Resume}
The MSL compiler can produces :
\begin{itemize}
\item A data parallel pattern of the multi-stencil application
\item \textcolor{gray}{An hybrid (data + task) pattern of the multi-stencil application}
\end{itemize}
\end{frame}
%----------------

@@

%-------------------------------------------------------------
\section{Conclusion and perspectives}
%-------------------------------------------------------------
\subsection{Conclusion and perspectives}
\begin{frame}
\frametitle{Conclusion}
\begin{block}{Conclusion}
\begin{itemize}
\item A DSL for Multi-Stencil applications (MSL)
\item The compilation of MSL to get data + task parallelism
\item The dump to a component-based runtime
\item Data parallelism evaluation: no overhead introduced 
\end{itemize}
\end{block}

\begin{block}{Perspectives}
\begin{itemize}
\item Scalability up to $32k$ cores on TGCC Curie (CEA)
\item Evaluations of the Data+Task parallelism (OpenMP 3)
\item Dynamic scheduling (OpenMP 4), CPU+GPU (Pochoir etc.)
\end{itemize}
$\hookrightarrow$ Show portability, maintainability introduced by components
\end{block}
\end{frame}
%-------------------------------------------------------------
